---
title: "Intro to bsyncr"
author: Cory Mosiman
date: "June 9th, 2020"
output: html_document
fontsize: 10pt
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

bsyncr is intended to be used in direct coordination with the [nmecr](https://github.com/kW-Labs/nmecr) package (even incorporating portions of nmecr into individual functions), enabling serialization of NMEC analysis into BuildingSync documents.  bsyncr has methods to:

- Create generic, high level BSync documents
- Utilize nmecr generated models
- Serialize important information about the models, including:
  - Baseline and Reporting periods
  - Which variable is being predicted (Reporting Variable), its units, and enduse
  - Which variables are the covariates (Explanatory Variables) and their units
  - The parameters of the model generated from the baseline period (DerivedModelParameters)
  - The performance of the model generated from the baseline period (DerivedModelPerformance)
  - Other model outputs


```{r setup, include=FALSE}
library(nmecr)
library(bsyncr)
```

## Stub out a Generic BSync Document

In general, the following workflow can be performed:

1. Generate a root document
2. Stub out a building, optionally providing an id for the building
3. Stub out two scenarios, a baseline and reporting scenario

```{r}
schema_loc <- "https://raw.githubusercontent.com/BuildingSync/schema/c620c7e58688698901edcb8560cd3e1b4b34d971/BuildingSync.xsd"
bsync_doc <- bsyncr::bs_gen_root_doc(schema_loc) %>%
  bsyncr::bs_stub_bldg(bldg_id = "My-Fav-Building") %>%
  bsyncr::bs_stub_scenarios(linked_building_id = "My-Fav-Building")
```

## Stub out a Baseline and Reporting Scenario

For both the Baseline and Reporting Scenarios:

1. Grab the scenario
2. Stub out the necessary contents for the Derived Model

```{r, results = 'hide'}
baseline_xpath <- "//auc:Scenario[auc:ScenarioType/auc:CurrentBuilding/auc:CalculationMethod/auc:Measured]"
reporting_xpath <- "//auc:Scenario[auc:ScenarioType/auc:PackageOfMeasures/auc:CalculationMethod/auc:Measured]"

sc_baseline <- xml2::xml_find_first(bsync_doc, baseline_xpath)
not_used <- sc_baseline %>% bsyncr::bs_stub_derived_model(dm_id = "DerivedModel-Baseline",
                                           dm_period = "Baseline",
                                           sc_type = "Current Building")

sc_reporting <- xml2::xml_find_first(bsync_doc, reporting_xpath)
not_used <- sc_reporting %>% bsyncr::bs_stub_derived_model(dm_id = "DerivedModel-Reporting",
                                           dm_period = "Reporting",
                                           sc_type = "Package of Measures")
```

# Generate nmecr model

Utilize the nmecr package to generate a simple linear regression (SLR) model.

```{r, results = 'hide'}
start_dt <- "03/01/2012 00:00"
end_dt <- "02/28/2013 23:59"
data_int <- "Daily"

b_df <- nmecr::create_dataframe(eload_data = nmecr::eload,
                                temp_data = nmecr::temp,
                                start_date = start_dt,
                                end_date = end_dt,
                                convert_to_data_interval = data_int)

SLR_model <- nmecr::model_with_SLR(b_df,
                                   nmecr::assign_model_inputs(regression_type = "SLR"))
```

# Serialize the nmecr model using bsyncr

```{r}
dm_base_xpath <- "//auc:DerivedModel[auc:DerivedModelPeriod = 'Baseline']/auc:DerivedModelInputs"
dm_baseline <- xml2::xml_find_first(bsync_doc,
                                    dm_base_xpath)

not_used <- bs_gen_dm_nmecr(nmecr_baseline_model = SLR_model,
                            x = dm_baseline)
```

# Write the file to output
```{r}
if (!dir.exists("output") ) {
  dir.create("output")
}
not_used <- xml2::write_xml(bsync_doc, "output/test1.xml")
```
